### 2019-11-01 usecases.tex
munzner ref added

\section{\noah Use Cases}
\label{sec:usage}
\new{Users prefer spreadsheets 
over enterprise solutions 
to view, explore, and analyze data~\cite{chan1996use,raden2005shedding}. 
To understand the scope of typical user 
tasks on spreadsheets, 
we make use of the typology 
of abstract data exploration tasks~\cite{brehmer2013multi}---see 
Table~\ref{tab:scope}. 
This typology characterizes the range of domain-independent
tasks performed on visual representations of data,
developed after analyzing task classification 
systems in over two dozen papers, 
and has been applied to a variety of 
scenarios, including \newsaj{analytical reasoning during exploration~\cite{shrinivasan2008supporting}, multi-dimensional data analysis~\cite{valiati2006taxonomy}, graph comprehension~\cite{friel2001making}, cartography~\cite{roth2012empirically}, among others.}\agp{argue for
 utility with citations.} \agp{This doesn't cut it because i wanted to argue that it HAS been used, not that it can be used. So can we find citations post 2013?.}
While all the tasks in Table~\ref{tab:scope} 
can be performed using spreadsheets, 
\noah enhances the experience 
for many of these tasks, 
indicated by a checkmark (\checkmark). 
We describe these tasks in the context
of a real usage scenario for \noah below.
Additional details regarding how \noah 
complements spreadsheets 
in accomplishing these tasks can be found in 
the Appendix.}

>>>>

\section{\noah Use Cases}
\label{sec:usage}
\new{Users prefer spreadsheets 
over enterprise solutions 
to view, explore, and analyze data~\cite{chan1996use,raden2005shedding}. 
To understand the scope of typical user 
tasks on spreadsheets, 
we make use of the typology 
of abstract data exploration tasks~\cite{brehmer2013multi}---see 
Table~\ref{tab:scope}. 
This typology characterizes the range of domain-independent
tasks performed on visual representations of data,
developed after analyzing task classification 
systems in over two dozen papers, 
and has been applied to a variety of 
scenarios, including \newsaj{visualization system design and validation models~\cite{meyer2015nested}, designing task taxonomy for cartograms~\cite{mcnabb2017survey}, and defining the scope of tasks in a number of domains, \eg interactive task authoring~\cite{fulda2015timelinecurator}, document mining~\cite{brehmer2014overview}, multivariate network analysis~\cite{pretorius2014tasks}, mass cytometry~\cite{hollt2016cytosplore}, among others.}\agp{argue for
 utility with citations.} \agp{This doesn't cut it because i wanted to argue that it HAS been used, not that it can be used. So can we find citations post 2013?.}
While all the tasks in Table~\ref{tab:scope} 
can be performed using spreadsheets, 
\noah enhances the experience 
for many of these tasks, 
indicated by a checkmark (\checkmark). 
We describe these tasks in the context
of a real usage scenario for \noah below.
Additional details regarding how \noah 
complements spreadsheets 
in accomplishing these tasks can be found in 
the Appendix.}
